\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} $|$ \textit{\small#3} & \href{#2}{Source Code} $|$ \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeActivitySubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} $|$ \textit{\small#3} & \textit{\small#2} $|$ \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ahmed Fathy} \\ \vspace{1pt}
    \small Software Engineer \\
    \href{mailto:ahmedfathi20044002@gmail.com}{\underline{ahmedfathi20044002@gmail.com}} $|$
    +20 155 285 1443 $|$
    \href{https://www.linkedin.com/in/ahmedfathy-x1}{\underline{LinkedIn}} $|$
    \href{https://github.com/ahmedfathy0-0}{\underline{GitHub}} $|$
    \href{https://www.mrfathi.tech/}{\underline{Portfolio}} $|$
    Haram, Giza, Egypt 12556
\end{center}


\section{Professional Summary}
  \small Detail-oriented Software Engineer with expertise in building full-stack web applications, RESTful APIs, and scalable backend architectures. Proven ability to optimize application performance and deploy robust solutions using modern technologies such as React, Node.js, and SQL databases.
  \vspace{8pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cairo University, Faculty of Engineering}{Giza, Egypt}
      {B.Sc. in Computer Engineering;  GPA: 3.6}{2022}
  \resumeSubHeadingListEnd
\section{Experience}
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {Al Nada Scientific Office}{Cairo, Egypt}{Technical Support Trainee}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Diagnostics \& Maintenance}
          {Troubleshot workstations and network equipment; performed firmware updates and preventive maintenance.}
        \resumeItem{Documentation}
          {Created systematic troubleshooting documentation to streamline hardware issue resolution.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectSubheading
      {Hankers (Social Platform)}{https://github.com/SWEProject25}{Full-Stack Engineering}{2025}
      \resumeItemListStart
        \resumeItem{Architecture}
          {Built scalable social platform using Microservices principles, React.js, and TypeScript.}
        \resumeItem{Frontend}
          {Implemented responsive UI design and asynchronous API integration via AJAX.}
        \resumeItem{DevOps}
          {Established CI/CD pipelines and containerized services using Docker for consistent deployment.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {NexaMart}{https://github.com/ahmedfathy0-0/NexaMart.git}{E-commerce Solution, Full-Stack}{2025}
      \resumeItemListStart
        \resumeItem{Stack}
          {Next.js (TypeScript), Redux Toolkit, Laravel 11, and MySQL.}
        \resumeItem{Functionality}
          {Implemented secure authentication (Sanctum), shopping cart logic, real-time order processing, and administrative analytics dashboard.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Company Manager App -- Al Nada Scientific Office}{https://github.com/Al-Nada-Company-Manager-App}{ERP System, React \& PostgreSQL}{2024}
      \resumeItemListStart
        \resumeItem{Tech Stack}
          {React.js, Redux, Express.js, Prisma, PostgreSQL, Electron for desktop deployment.}
        \resumeItem{Business Solution}
          {Developed ERP application for Al Nada Scientific Office managing customers, suppliers, inventory, and sales records.}
        \resumeItem{Deployment}
          {Packaged application with Electron for local server deployment, enabling offline usage.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Tayseer-Web}{https://github.com/ahmedfathy0-0/Tayseer-web.git}{Corporate Web Solution, Next.js}{2024}
      \resumeItemListStart
        \resumeItem{Deployment}
          {Deployed corporate website utilizing Next.js framework and TypeScript.}
        \resumeItem{Performance}
          {Maximized performance via Server-Side Rendering (SSR) and strict static typing for reliability.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Interactive Orrery -- NASA Space Apps Hackathon}{https://github.com/ahmedfathy0-0/Pharoh-s-StarCode}{3D Space Simulation, React.js}{Oct 2024}
      \resumeItemListStart
        \resumeItem{Hackathon Project}
          {Developed during NASA Space Apps Challenge 2024, simulating orbital mechanics and near-Earth object trajectories using React.js and Three.js.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Image Restoration Pipeline}{https://github.com/ahmedfathy0-0/Image-Colorization-of-Historical-Photos}{Deep Learning \& Computer Vision, Python}{2024}
      \resumeItemListStart
        \resumeItem{Pipeline}
          {Constructed end-to-end restoration pipeline: Denoising, Deblurring, and Inpainting.}
        \resumeItem{Algorithms}
          {Applied Telea (FMM) inpainting and deep learning models to restore damaged historical photographs.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Blog Web Application}{https://github.com/ahmedfathy0-0/Pharoh-s-StarCode}{Content Management System, Node.js}{2024}
      \resumeItemListStart
        \resumeItem{Core Features}
          {Architected content platform with CRUD capabilities, rich-text editing (Quill), and secure image handling (Multer).}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Path Planning Analysis}{https://github.com/ahmedfathy0-0/Path-Planing-Analysis}{Algorithm Benchmarking, C++}{2024}
      \resumeItemListStart
        \resumeItem{Performance}
          {Benchmarked pathfinding algorithms (A*, Dijkstra, RRT) analyzing computational complexity and execution time.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {x86 Brick Breakers Arcade}{https://github.com/ahmedfathy0-0/Brick-Breakers-Game-Assembly-8086.git}{Assembly (x86), MASM, Low-Level Programming}{2024}
      \resumeItemListStart
        \resumeItem{Game Logic}
          {Developed a real-time, multiplayer arcade game using x86 Assembly and the MASM assembler.}
        \resumeItem{System Control}
          {Directly manipulated video memory for low-latency graphics rendering and managed hardware interrupts to handle real-time I/O.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Alien Invasion}{https://github.com/ahmedfathy0-0/alien-invasion}{Combat Simulation, C++}{2023}
      \resumeItemListStart
        \resumeItem{Simulation}
          {Modeled combat scenarios using custom data structures to simulate fleet mechanics and collision detection.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Paint For Kids}{https://github.com/ahmedfathy0-0/paint-app}{C++, OOP, Data Structures}{2023}
      \resumeItemListStart
        \resumeItem{Application}
          {Built desktop drawing application with shape tools, color fills, and interactive game modes.}
        \resumeItem{Design}
          {Applied OOP principles using polymorphism for extensible shape classes and Stack-based Undo/Redo system.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Tactic (Robotics \& AI)}{https://github.com/roboSobia}{Embedded Systems}{2024}
      \resumeItemListStart
        \resumeItem{System Integration}
          {Developed browser-controlled robotics suite integrating AI computer vision with low-latency hardware control.}
        \resumeItem{Firmware}
          {Programmed ESP32 microcontrollers to handle WebSocket communication for real-time motor control and telemetry.}
        \resumeItem{Backend Processing}
          {Deployed YOLOv5 and OpenCV on host server to process visual feedback and automate robotic decision-making.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {AES Encryption/Decryption Engine}{https://github.com/ahmedfathy0-0/AES.git}{Verilog, FPGA, Cryptography}{2023}
      \resumeItemListStart
        \resumeItem{Core Logic}
          {Synthesized robust AES cryptographic core in Verilog HDL supporting 128-bit, 192-bit, and 256-bit key standards.}
        \resumeItem{Datapath}
          {Engineered hardware-optimized modules for SubBytes, ShiftRows, MixColumns, and AddRoundKey transformations.}
        \resumeItem{Validation}
          {Verified cryptographic correctness against standard NIST test vectors using rigorous debug tracing.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {CNN Convolution Accelerator}{https://github.com/AhmedSobhy01/convolution-accelerator.git}{Verilog, OpenLane2, ASIC Design}{2025}
      \resumeItemListStart
        \resumeItem{Architecture}
          {Designed a synthesizable 2D convolution accelerator using Systolic Arrays and fully pipelined dataflow to maximize MAC throughput.}
        \resumeItem{Memory Hierarchy}
          {Implemented DMA-based loading and dual-port SRAM buffering to support up to 16x16 kernel execution.}
        \resumeItem{Physical Design}
          {Executed RTL-to-GDSII synthesis using OpenLane2, validating physical feasibility and achieving timing closure.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {5-Stage Pipelined Processor (RISC)}{https://github.com/Exo1i/5-Stage-Pipelined-Processor.git}{VHDL, QuestaSim, Computer Architecture}{2025}
      \resumeItemListStart
        \resumeItem{Core Architecture}
          {Engineered a 32-bit 5-stage pipelined processor in VHDL, supporting a custom ISA of over 25 instructions.}
        \resumeItem{Hazard Resolution}
          {Optimized throughput by implementing Hazard Detection and Data Forwarding units to resolve control and data dependencies.}
        \resumeItem{Verification}
          {Validated functional correctness through rigorous simulation and testbench environments in QuestaSim.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Student Activities}
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {IEEE}{Cairo}{UI/UX Designer - Frontend Team Leader}{Oct 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Portfolio Platform Development}
          {Engineered comprehensive web platform featuring workshop and event management systems with admin dashboard for content creation, role-based access control enabling instructors to upload course materials and students to register for workshops and events.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeActivitySubheading
      {Technical Center for Career Development (TCCD)}{Cairo}{Frontend Developer}{June 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Portfolio Platform Development}
          {Developed comprehensive platform with event pages, admin dashboard for event creation, role-based access for instructors and students, location management, event galleries, and statistical analysis pages.}
        \resumeItem{HR Management \& Judging System}
          {Built HR system managing team attendance with custom form builder and reviewer functionality similar to Google Forms, alongside event judging system for evaluating and assessing teams applying to events.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeActivitySubheading
      {Physics Helping District (PhD)}{Cairo}{Team Leader}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Mentorship}
          {Led peer tutoring initiative in electronics, achieving measurable academic improvement.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeActivitySubheading
      {NASA Space Apps Challenge}{Cairo}{Participant -- Project: "Orrery"}{Oct 2024}
      \resumeItemListStart
        \resumeItem{Orrery App}
          {Developed an interactive orrery app visualizing near-Earth objects using React and Three.js.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Technical Skills}
 \resumeSubHeadingListStart
    \item{\textbf{Programming Languages}{: TypeScript, JavaScript, Python, C++, PHP, SQL, VHDL, Verilog}}
    \item{\textbf{Frontend Engineering}{: React.js, Next.js, Redux Toolkit, Tailwind CSS, Material-UI, Three.js}}
    \item{\textbf{Backend \& Database}{: Node.js, Express.js, Laravel, FastAPI, PostgreSQL, MySQL, MongoDB, Prisma ORM}}
    \item{\textbf{AI \& Computer Vision}{: OpenCV, YOLOv5, NumPy, Pandas, Scikit-learn, PyTorch}}
    \item{\textbf{DevOps \& Tools}{: Docker, Git/GitHub, CI/CD Pipelines, Linux (Bash), Postman, Agile/Scrum}}
 \resumeSubHeadingListEnd

\end{document}
