\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} $|$ \textit{\small#3} & \href{#2}{Source Code} $|$ \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeActivitySubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} $|$ \textit{\small#3} & \textit{\small#2} $|$ \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ahmed Fathy} \\ \vspace{1pt}
    \small Software Engineer \\
    \href{mailto:ahmedfathi20044002@gmail.com}{\underline{ahmedfathi20044002@gmail.com}} $|$
    +20 155 285 1443 $|$
    \href{https://www.linkedin.com/in/ahmedfathy-x1}{\underline{LinkedIn}} $|$
    \href{https://github.com/ahmedfathy0-0}{\underline{GitHub}} $|$
    \href{https://www.mrfathi.tech/}{\underline{Portfolio}} $|$
    Haram, Giza, Egypt 12556
\end{center}


\section{Professional Summary}
  \small Detail-oriented Software Engineer with expertise in building full-stack web applications, RESTful APIs, and scalable backend architectures. Proven ability to optimize application performance and deploy robust solutions using modern technologies such as React, Node.js, and SQL databases.
  \vspace{8pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {Al Nada Scientific Office}{Cairo, Egypt}{Software Developer (Part-time)}{June 2022 -- 2025}
      \resumeItemListStart
        \resumeItem{ERP System}
          {Developed a local desktop application (packaged with Electron) managing customers, suppliers, inventory, and sales records using React.js, Express.js, and PostgreSQL.}
        \resumeItem{Corporate Web Solution}
          {Built the official company website integrated with an e-commerce platform designed to seamlessly manage and showcase sponsors, partners, services, and dynamic product catalogs.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectSubheading
      {Hankers (Social Platform)}{https://github.com/SWEProject25}{Full-Stack Engineering}{2025}
      \resumeItemListStart
        \resumeItem{Architecture}
          {Built scalable social platform using Microservices principles, React.js, and TypeScript.}
        \resumeItem{Frontend}
          {Implemented responsive UI design and asynchronous API integration via AJAX.}
        \resumeItem{DevOps}
          {Established CI/CD pipelines and containerized services using Docker for consistent deployment.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {TCCD Official Website \& Management System}{https://tccd.eng.cu.edu.eg/}{Full-Stack Development | React,Typescript}{2026}
      \resumeItemListStart
        \resumeItem{Impact}
          {Developed a comprehensive student activity platform that successfully scaled to support and manage over 20,000 active users.}
        \resumeItem{Core Features}
          {Engineered a robust event and judging system that handles registration slots, waiting lists, and distinct role-based access for members, standard users, and corporate entities.}
        \resumeItem{Administration}
          {Built an advanced admin dashboard equipped with user-facing analytics to streamline the management of events, user data, and company profiles.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Interactive Orrery -- NASA Space Apps Hackathon}{https://github.com/ahmedfathy0-0/Pharoh-s-StarCode}{3D Space Simulation, React.js}{Oct 2024}
      \resumeItemListStart
        \resumeItem{Hackathon Project}
          {Developed during NASA Space Apps Challenge 2024, simulating orbital mechanics and near-Earth object trajectories using React.js and Three.js.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Ocean Adventure: Grand Tide (3D Survival RPG)}{https://github.com/ahmedfathy0-0/Grand-Tide}{C++, OpenGL, GLSL}{2026}
      \resumeItemListStart
        \resumeItem{Graphics \& Rendering}
          {Built a custom 3D rendering engine utilizing a Forward Renderer with transparent object sorting, Phong shading models, and post-processing effects.}
        \resumeItem{Shader Programming}
          {Implemented custom GLSL shaders, including a dynamic water shader featuring Fresnel reflections, refraction mapping, and summed sine wave displacement.}
        \resumeItem{Architecture \& Logic}
          {Engineered a lightweight Entity-Component-System (ECS) to handle 3D meshes, bounding-box collision detection, ray-casting combat, and procedural entity generation.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Image Restoration Pipeline}{https://github.com/ahmedfathy0-0/Image-Colorization-of-Historical-Photos}{Deep Learning \& Computer Vision, Python}{2024}
      \resumeItemListStart
        \resumeItem{Pipeline}
          {Constructed end-to-end restoration pipeline: Denoising, Deblurring, and Inpainting.}
        \resumeItem{Algorithms}
          {Applied Telea (FMM) inpainting and deep learning models to restore damaged historical photographs.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {NexaMart}{https://github.com/ahmedfathy0-0/NexaMart.git}{E-commerce Solution, Full-Stack}{2025}
      \resumeItemListStart
        \resumeItem{Stack}
          {Next.js (TypeScript), Redux Toolkit, Laravel 11, and MySQL.}
        \resumeItem{Functionality}
          {Implemented secure authentication (Sanctum), shopping cart logic, real-time order processing, and administrative analytics dashboard.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cairo University, Faculty of Engineering}{Giza, Egypt}
      {B.Sc. in Computer Engineering;  GPA: 3.6}{2022}
  \resumeSubHeadingListEnd
\section{Student Activities}
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {IEEE}{Cairo}{UI/UX Designer - Frontend Team Leader}{Oct 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Portfolio Platform Development}
          {Engineered comprehensive web platform featuring workshop and event management systems with admin dashboard for content creation, role-based access control enabling instructors to upload course materials and students to register for workshops and events.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeActivitySubheading
      {Technical Center for Career Development (TCCD)}{Cairo}{Frontend Developer}{June 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Portfolio Platform Development}
          {Developed comprehensive platform with event pages, admin dashboard for event creation, role-based access for instructors and students, location management, event galleries, and statistical analysis pages.}
        \resumeItem{HR Management \& Judging System}
          {Built HR system managing team attendance with custom form builder and reviewer functionality similar to Google Forms, alongside event judging system for evaluating and assessing teams applying to events.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeActivitySubheading
      {Physics Helping District (PhD)}{Cairo}{Team Leader}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Mentorship}
          {Led peer tutoring initiative in electronics, achieving measurable academic improvement.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeActivitySubheading
      {NASA Space Apps Challenge}{Cairo}{Participant -- Project: "Orrery"}{Oct 2024}
      \resumeItemListStart
        \resumeItem{Orrery App}
          {Developed an interactive orrery app visualizing near-Earth objects using React and Three.js.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Technical Skills}
 \resumeSubHeadingListStart
    \item{\textbf{Programming Languages}{: C++ Programming, Python, JavaScript, TypeScript, SQL, PHP, Java, Assembly Language, OpenGL, GLSL}}
    \item{\textbf{Core Computing Concepts}{: Data Structures, Algorithms, Object-Oriented Programming, Design Patterns, Operating Systems, System Architecture, Cryptography}}
    \item{\textbf{Systems Programming}{: Unix/Linux Development, Multithreading, Memory Management, Network Socket Programming}}
    \item{\textbf{Backend Development \& DevOps}{: Node.js Runtime, Express Framework, Laravel, RESTful APIs, Docker Containers, Git Version Control, CI/CD Pipelines}}
 \resumeSubHeadingListEnd

\end{document}
