\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} $|$ \textit{\small#2} & #3 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeActivitySubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} $|$ \textit{\small#3} & \textit{\small#2} $|$ \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ahmed Fathy} \\ \vspace{1pt}
    \small Software Engineer \\
    \href{mailto:ahmedfathi20044002@gmail.com}{\underline{ahmedfathi20044002@gmail.com}} $|$
    +20 155 285 1443 $|$
    \href{https://www.linkedin.com/in/ahmedfathy-x1}{\underline{LinkedIn}} $|$
    \href{https://github.com/ahmedfathy0-0}{\underline{GitHub}} $|$
    \href{https://www.mrfathi.tech/}{\underline{Portfolio}} $|$
    Haram, Giza, Egypt 12556
\end{center}


\section{Professional Summary}
  \small Detail-oriented Software Engineer with expertise in building full-stack web applications, RESTful APIs, and scalable backend architectures. Proven ability to optimize application performance and deploy robust solutions using modern technologies such as React, Node.js, and SQL databases.
  \vspace{8pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cairo University, Faculty of Engineering}{Giza, Egypt}
      {B.Sc. in Computer Engineering;  GPA: 3.7}{2022}
  \resumeSubHeadingListEnd
\section{Experience}
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {Al Nada Scientific Office}{Cairo, Egypt}{Technical Support Trainee}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Diagnostics \& Maintenance}
          {Troubleshot workstations and network equipment; performed firmware updates and preventive maintenance.}
        \resumeItem{Documentation}
          {Created systematic troubleshooting documentation to streamline hardware issue resolution.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectSubheading
      {5-Stage Pipelined Processor (RISC)}{VHDL, QuestaSim, Computer Architecture}{\href{https://github.com/Exo1i/5-Stage-Pipelined-Processor.git}{Source Code} $|$ \textit{\small 2025}}
      \resumeItemListStart
        \resumeItem{Core Architecture}
          {Engineered a 32-bit 5-stage pipelined processor in VHDL, supporting a custom ISA of over 25 instructions.}
        \resumeItem{Hazard Resolution}
          {Optimized throughput by implementing Hazard Detection and Data Forwarding units to resolve control and data dependencies.}
        \resumeItem{Verification}
          {Validated functional correctness through rigorous simulation and testbench environments in QuestaSim.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {CNN Convolution Accelerator}{Verilog, OpenLane2, ASIC Design}{\href{https://github.com/AhmedSobhy01/convolution-accelerator.git}{Source Code} $|$ \textit{\small 2025}}
      \resumeItemListStart
        \resumeItem{Architecture}
          {Designed a synthesizable 2D convolution accelerator using Systolic Arrays and fully pipelined dataflow to maximize MAC throughput.}
        \resumeItem{Memory Hierarchy}
          {Implemented DMA-based loading and dual-port SRAM buffering to support up to 16x16 kernel execution.}
        \resumeItem{Physical Design}
          {Executed RTL-to-GDSII synthesis using OpenLane2, validating physical feasibility and achieving timing closure.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {AES Encryption/Decryption Engine}{Verilog, FPGA, Cryptography}{\href{https://github.com/ahmedfathy0-0/AES.git}{Source Code} $|$ \textit{\small 2023}}
      \resumeItemListStart
        \resumeItem{Core Logic}
          {Synthesized robust AES cryptographic core in Verilog HDL supporting 128-bit, 192-bit, and 256-bit key standards.}
        \resumeItem{Datapath}
          {Engineered hardware-optimized modules for SubBytes, ShiftRows, MixColumns, and AddRoundKey transformations.}
        \resumeItem{Validation}
          {Verified cryptographic correctness against standard NIST test vectors using rigorous debug tracing.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Tactic (Robotics \& AI)}{Embedded Systems}{\href{https://github.com/roboSobia}{Source Code} $|$ \textit{\small 2024}}
      \resumeItemListStart
        \resumeItem{System Integration}
          {Developed browser-controlled robotics suite integrating AI computer vision with low-latency hardware control.}
        \resumeItem{Firmware}
          {Programmed ESP32 microcontrollers to handle WebSocket communication for real-time motor control and telemetry.}
        \resumeItem{Backend Processing}
          {Deployed YOLOv5 and OpenCV on host server to process visual feedback and automate robotic decision-making.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {Hankers (Social Platform)}{Full-Stack Engineering}{\href{https://github.com/SWEProject25}{Source Code} $|$ \textit{\small 2025}}
      \resumeItemListStart
        \resumeItem{Architecture}
          {Built scalable social platform using Microservices principles, React.js, and TypeScript.}
        \resumeItem{Frontend}
          {Implemented responsive UI design and asynchronous API integration via AJAX.}
        \resumeItem{DevOps}
          {Established CI/CD pipelines and containerized services using Docker for consistent deployment.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {TCCD Official Website \& Management System}{Frontend Development | React,Typescript}{\href{https://tccd.eng.cu.edu.eg/}{Live Preview} $|$ \textit{\small 2026}}
      \resumeItemListStart
        \resumeItem{Impact}
          {Developed a comprehensive student activity platform that successfully scaled to support and manage over 20,000 active users.}
        \resumeItem{Core Features}
          {Engineered a robust event and judging system that handles registration slots, waiting lists, and distinct role-based access for members, standard users, and corporate entities.}
        \resumeItem{Administration}
          {Built an advanced admin dashboard equipped with user-facing analytics to streamline the management of events, user data, and company profiles.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Student Activities}
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {IEEE}{Cairo}{UI/UX Designer - Frontend Team Leader}{Oct 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Portfolio Platform Development}
          {Engineered comprehensive web platform featuring workshop and event management systems with admin dashboard for content creation, role-based access control enabling instructors to upload course materials and students to register for workshops and events.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeActivitySubheading
      {Technical Center for Career Development (TCCD)}{Cairo}{Frontend Developer}{June 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Portfolio Platform Development}
          {Built an integrated portfolio, event management, HR, and judging system with role-based access, dashboards, analytics, attendance tracking, custom forms, and evaluation workflows to streamline operations and decision-making.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeActivitySubheading
      {Physics Helping District (PhD)}{Cairo}{Team Leader}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Mentorship}
          {Led peer tutoring initiative in electronics, achieving measurable academic improvement.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeActivitySubheading
      {NASA Space Apps Challenge}{Cairo}{Participant -- Project: "Orrery"}{Oct 2024}
      \resumeItemListStart
        \resumeItem{Orrery App}
          {Developed an interactive orrery app visualizing near-Earth objects using React and Three.js.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Technical Skills}
 \resumeSubHeadingListStart
    \item{\textbf{Digital Design \& Verification}{: Verilog HDL, VHDL, RTL Design, RISC-V ISA, MIPS Architecture, Pipeline Design, RTL-to-GDSII Flow, OpenLane2, DRC/LVS Verification, Static Timing Analysis, FSM Design}}
    \item{\textbf{Development Tools \& Platforms}{: ModelSim, QuestaSim, Intel Quartus Prime, GTKWave, ESP32, AVR/Arduino}}
    \item{\textbf{Programming Languages}{: C/C++ (Advanced), Python, x86 Assembly, MIPS Assembly}}
 \resumeSubHeadingListEnd

\end{document}
