\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\linespread{0.97}\selectfont
\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=2pt,parsep=0pt,partopsep=0pt}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} $|$ \textit{\small#2} & #3 \\
    \end{tabular*}\vspace{-13pt}
}

\newcommand{\resumeActivitySubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} $|$ \textit{\small#3} & \textit{\small#2} $|$ \textit{\small #4} \\
    \end{tabular*}\vspace{-13pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\vspace*{0.3pt}\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=1.2pt,parsep=0pt,partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ahmed Fathy} \\ \vspace{1pt}
    \small Software Engineer \\
    \href{mailto:ahmedfathi20044002@gmail.com}{\underline{ahmedfathi20044002@gmail.com}} $|$
    +20 155 285 1443 $|$
    \href{https://www.linkedin.com/in/ahmedfathy-x1}{\underline{LinkedIn}} $|$
    \href{https://github.com/ahmedfathy0-0}{\underline{GitHub}} $|$
    \href{https://www.mrfathi.tech/}{\underline{Portfolio}} $|$
    Haram, Giza, Egypt 12556
\end{center}


\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cairo University, Faculty of Engineering}{Giza, Egypt}
      {B.Sc. in Computer Engineering;  GPA: 3.7}{2022 -- 2027}
  \resumeSubHeadingListEnd
  \vspace{-2pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {Al Nada Scientific Office}{Cairo, Egypt}{Software Developer (Part-time)}{June 2022 -- 2025}
      \resumeItemListStart
        \resumeItem{ERP System}
          {Developed a local desktop application (packaged with Electron) managing customers, suppliers, inventory, and sales records using React.js, Express.js, and PostgreSQL.}
        \resumeItem{Corporate Web Solution}
          {Built the official company website integrated with an e-commerce platform designed to seamlessly manage and showcase sponsors, partners, services, and dynamic product catalogs.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-2pt}
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectSubheading
      {\href{https://github.com/Exo1i/5-Stage-Pipelined-Processor.git}{\textbf{5-Stage Pipelined Processor (RISC)}}}{VHDL, QuestaSim, Computer Architecture}{\textit{\small 2025}}
      \resumeItemListStart
        \resumeItem{Core Architecture}
          {Engineered a 32-bit 5-stage pipelined processor in VHDL, supporting a custom ISA of over 25 instructions.}
        \resumeItem{Hazard Resolution}
          {Optimized throughput by implementing Hazard Detection and Data Forwarding units to resolve control and data dependencies.}
        \resumeItem{Verification}
          {Validated functional correctness through rigorous simulation and testbench environments in QuestaSim.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {\href{https://github.com/AhmedSobhy01/convolution-accelerator.git}{\textbf{CNN Convolution Accelerator}}}{Verilog, OpenLane2, ASIC Design}{\textit{\small 2025}}
      \resumeItemListStart
        \resumeItem{Architecture}
          {Designed a synthesizable 2D convolution accelerator using Systolic Arrays and fully pipelined dataflow to maximize MAC throughput.}
        \resumeItem{Memory Hierarchy}
          {Implemented DMA-based loading and dual-port SRAM buffering to support up to 16x16 kernel execution.}
        \resumeItem{Physical Design}
          {Executed RTL-to-GDSII synthesis using OpenLane2, validating physical feasibility and achieving timing closure.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {\href{https://github.com/ahmedfathy0-0/AES.git}{\textbf{AES Encryption/Decryption Engine}}}{Verilog, FPGA, Cryptography}{\textit{\small 2023}}
      \resumeItemListStart
        \resumeItem{Core Logic}
          {Synthesized robust AES cryptographic core in Verilog HDL supporting 128-bit, 192-bit, and 256-bit key standards.}
        \resumeItem{Datapath}
          {Engineered hardware-optimized modules for SubBytes, ShiftRows, MixColumns, and AddRoundKey transformations.}
        \resumeItem{Validation}
          {Verified cryptographic correctness against standard NIST test vectors using rigorous debug tracing.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {\href{https://github.com/roboSobia}{\textbf{Tactic (Robotics \& AI)}}}{Embedded Systems}{\textit{\small 2024}}
      \resumeItemListStart
        \resumeItem{System Integration}
          {Developed browser-controlled robotics with AI vision and low-latency control}
        \resumeItem{Firmware}
          {Programmed ESP32 microcontrollers to handle WebSocket communication for real-time motor control.}
        \resumeItem{Backend Processing}
          {Deployed YOLOv5 and OpenCV on host server to process visual feedback and automate robotic decision-making.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {\href{https://github.com/SWEProject25}{\textbf{Hankers (Social Platform)}}}{Full-Stack Engineering}{\textit{\small 2025}}
      \resumeItemListStart
        \resumeItem{Architecture}
          {Built scalable social platform using Microservices principles, React.js, and TypeScript.}
        \resumeItem{Frontend}
          {Implemented responsive UI design and asynchronous API integration via AJAX.}
        \resumeItem{DevOps}
          {Established CI/CD pipelines and containerized services using Docker for consistent deployment.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {\href{https://github.com/ahmedfathy0-0/Brick-Breakers-Game-Assembly-8086.git}{\textbf{x86 Brick Breakers Arcade}}}{Assembly (x86), MASM, Low-Level Programming}{\textit{\small 2024}}
      \resumeItemListStart
        \resumeItem{Game Logic}
          {Developed a real-time, multiplayer arcade game using x86 Assembly and the MASM assembler.}
        \resumeItem{System Control}
          {Directly manipulated video memory for low-latency graphics rendering and managed hardware interrupts to handle real-time I/O.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeProjectSubheading
      {\href{https://github.com/ahmedfathy0-0/alien-invasion}{\textbf{Alien Invasion}}}{Combat Simulation, C++}{\textit{\small 2023}}
      \resumeItemListStart
        \resumeItem{Simulation}
          {Modeled combat scenarios using custom data structures to simulate fleet mechanics and collision detection.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-2pt}
\section{Student Activities}
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {IEEE}{Cairo}{UI/UX Designer - Frontend Team Leader}{Oct 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Portfolio Platform Development}
          {Engineered comprehensive web platform featuring workshop and event management systems with admin dashboard for content creation, role-based access control enabling instructors to upload course materials and students to register for workshops and events.}
      \resumeItemListEnd
    \vspace{4pt}
    \resumeActivitySubheading
      {NASA Space Apps Challenge}{Cairo}{Participant -- Project: "Orrery"}{Oct 2024}
      \resumeItemListStart
        \resumeItem{Orrery App}
          {Developed an interactive orrery app visualizing near-Earth objects using React and Three.js.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-2pt}
\section{Technical Skills}
 \resumeSubHeadingListStart
    \item{\textbf{Digital Design \& Verification}{: Verilog HDL, VHDL, RTL Design, RISC-V ISA, MIPS Architecture, Pipeline Design, RTL-to-GDSII Flow, OpenLane2, DRC/LVS Verification, Static Timing Analysis, FSM Design}}
    \item{\textbf{Development Tools \& Platforms}{: ModelSim, QuestaSim, Intel Quartus Prime, GTKWave, ESP32, AVR/Arduino}}
    \item{\textbf{Programming Languages}{: C/C++ (Advanced), Python, x86 Assembly, MIPS Assembly}}
 \resumeSubHeadingListEnd
 \vspace{-2pt}

\end{document}
